Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2022-11-28 ms/ms03_results.tex
MS

\subsection*{Trait, eQTL gene and tissue frequency of individual eQTLs in pleiotropic regions}

In Figure \ref{fig:region_gwas_egenes_tissues}, I have plotted the number of trait classes, eQTL genes and tissues of
eQTLs in three pleiotropic regions.
%
All three regions are very pleiotropic with very different associated trait classes such as cancer, cardiovascular and
autoimmune diseases (Table \ref{tab:pleiotropic_regions} and Supplementary table 5).
%
However these plots show that the relationship between pleiotropy and the number of eQTL genes and tissues is not direct.

Some regions have high number of eQTL genes and intermediate number of tissues like the interleukin locus in region 5:131912097-132802472 (5q31.1),
intermediate number of eQTL gene and variable number of tissues like the 11:65488118-65916060 locus (11q13.1),
high number of both eQTL genes and tissues like the 12:55,721,801-56,171,027 (12q13.2) region
and relatively low number of eQTL genes and tissue like the 19:48,668,049-48,756,272 locus (19q13.33) (Fig. \ref{fig:region_gwas_egenes_tissues}).

In summary, trait pleiotropy can arise in locus with variable absolute numbers of genes and tissues.

@@

In the following sections, I wonder about the the molecular mechanism of pleiotropic eQTLs.
%
%I hypothesized that pleiotropy arises from bias in regulatory effects of variants.
%%
%For instance, pleiotropic variants might significantly affect some molecular functions more often.
%%
%Another possibility is that pleiotropic variants affect more eGenes in more eTissues, which affect more GWAS traits.

First, I analysed whether there are significant differences of some effect consequences between more and less pleiotropic variants.
%
I separated variants according to the count of GWAS classes and computed the EBI variant effect predictor (VEP) consequence (\citep{2016.Cunningham.McLaren}).
%
I found a significant larger number of upstream, 5'-UTR, downstream and 3'-UTR variants
with 2, 3 and 4 and more classes compared to variants with one class (Fig. \ref{fig:vep_consequence}).
%
I also found a significant larger number of intron, and non-coding transcript variants
with 3 and 4 and more classes (Fig. \ref{fig:vep_consequence}).
%
These analyses suggest that more pleiotropic variants have a stronger effect on
the coding sequence and splicing regions, which might explain partly their more pleiotropic function.

@@

Then I hypothesized that pleiotropic variants modulate more genes even within the same tissues.
%
To test this hypothesis, I computed the number of eQTL genes per variant-tissue pair for different trait class counts.
%
%If the GWAS class count of a variant changed in different variant-eGene-eTissue trios, then we kept the maximal one.
%
eQTLs involved in 1, 2, 3, 4, and 5 and more GWAS classes modulate an average of 1.3, 1.5, 1.6, 1.9 and 1.8 genes, respectively (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%I found means of eGene counts of 1.4, 1.7, 1.7 and 1.6 for GWAS classes counts 5, 4, 3 and 2 compared to eGene count mean of 1.5 for GWAS class count 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This suggests that pleiotropic eQTLs modulate more genes compared to eQTLs involved in only one GWAS class (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
More target genes of eQTLs provides an explanation to the observed pleiotropy.

@@

My next hypothesis was that pleiotropic eQTL-gene pairs are active in more tissues than non-pleiotropic eQTLs.
%
To test this hypothesis, the tissues per eQTL-gene pair was counted for eQTL involved in different GWAS class counts.
%
eQTLs involved in 1, 2, 3, 4, and 5 and more GWAS classes are active in an average of 2.4, 2.5, 2.8, 3.4 and 4.3 tissues, respectively (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This suggests that pleiotropic eQTL are active in more tissues (Mann–Whitney U test) compared to non-pleiotropic eQTLs (Fig. \ref{fig:gwas_egene_etisue_per_variant}b).

@@

In Fig. \ref{fig:gwas_egene_etisue_per_variant}b, I observed that pairs of eQTL-gene are active in more tissues.
%
To explain this observation, I hypothesized that pleiotropic eQTLs are active in more tissues,
because genomic regions around pleiotropic variants bind more transcription factors,
which upregulate the pleiotropic regions in more tissues.
%
To test this hypothesis, I counted the number of unique transcription factors bound in a radius of 50 bp around each eQTL (Window of 100 bp).
%
eQTLs involved in 1, 2, 3 and 4 and more GWAS classes bind a mean number of 17,
19, 23 and 27 transcription factors, respectively (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%I found a significant larger number of transcription factors bound around pleiotropic variants (Fig. \ref{fig:freq_tf_per_variant}a).

>>>>

\subsection*{Relation between trait, eQTL gene and tissue counts}

In Supplementary Figure \ref{fig:region_gwas_egenes_tissues}, I have plotted the number of trait classes, eQTL genes and tissues of
eQTLs in four pleiotropic regions.
%
All three regions are very pleiotropic with very different associated trait classes such as cancer, cardiovascular and
autoimmune diseases (Table \ref{tab:pleiotropic_regions} and Supplementary table 5).
%
However these plots show that the relationship between pleiotropy and the number of eQTL genes and tissues is not direct.
%
These plots suggest that counts of eQTL genes and tissues per variant correlate better between them than with the counts of the trait classes.
%
Indeed, Spearman correlation between eQTL gene and tissue counts is 0.75 while their correlation with the count of GWAS classes is 0.29 and 0.25, respectively (Fig. \ref{fig:region_gwas_egenes_tissues}).

In summary, counts of eQTL genes and tissues is highly correlated, while correlation with GWAS classes is much lower.

@@

In the following sections, I studied different molecular mechanisms of pleiotropic eQTLs.
%
%I hypothesized that pleiotropy arises from bias in regulatory effects of variants.
%%
%For instance, pleiotropic variants might significantly affect some molecular functions more often.
%%
%Another possibility is that pleiotropic variants affect more eGenes in more eTissues, which affect more GWAS traits.

First, I analysed whether there are significant differences of some effect consequences between more and less pleiotropic eQTLs.
%
I separated eQTLs according to the count of GWAS classes and computed the EBI variant effect predictor (VEP) consequence (\citep{2016.Cunningham.McLaren}).
%
I found a significant larger number of upstream, 5'-UTR, downstream and 3'-UTR eQTLs
with 2, 3 and 4 and more classes compared to eQTLs with one class (Fig. \ref{fig:vep_consequence}).
%
I also found a significant larger number of intron, and non-coding transcript eQTLs
with 3 and 4 and more classes (Fig. \ref{fig:vep_consequence}).
%
These analyses suggest that more pleiotropic eQTLs have a stronger effect on
the coding sequence and splicing regions, which might explain partly their more pleiotropic function.

@@

Then I hypothesized that pleiotropic eQTLs modulate more genes even after taking into account the same tissues.
%
To test this hypothesis, I computed the number of eQTL genes per eQTL-tissue pair for different trait class counts.
%
%If the GWAS class count of a variant changed in different variant-eGene-eTissue trios, then we kept the maximal one.
%
eQTLs involved in 1, 2, 3, 4, and 5 and more GWAS classes modulate an average of 1.3, 1.5, 1.6, 1.9 and 1.8 genes, respectively (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%I found means of eGene counts of 1.4, 1.7, 1.7 and 1.6 for GWAS classes counts 5, 4, 3 and 2 compared to eGene count mean of 1.5 for GWAS class count 1 (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This suggests that pleiotropic eQTLs modulate more genes compared to eQTLs involved in only one GWAS class (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
More target genes of eQTLs provides an explanation to the observed pleiotropy.

@@

My next hypothesis was that pleiotropic eQTL-gene pairs are active in more tissues than non-pleiotropic eQTLs.
%
To test this hypothesis, the number of tissues per eQTL-gene pair was counted for eQTL involved in different GWAS class counts.
%
eQTLs involved in 1, 2, 3, 4, and 5 and more GWAS classes are active in an average of 2.4, 2.5, 2.8, 3.4 and 4.3 tissues, respectively (Fig. \ref{fig:gwas_egene_etisue_per_variant}a).
%
This suggests that pleiotropic eQTL are active in more tissues (Mann–Whitney U test) compared to non-pleiotropic eQTLs (Fig. \ref{fig:gwas_egene_etisue_per_variant}b).

@@

In Fig. \ref{fig:gwas_egene_etisue_per_variant}b, I observed that pairs of eQTL-gene are active in more tissues.
%
One explanation might be that pleiotropic eQTLs bound by more transcription factors, which in turn, upregulate the pleiotropic eQTLs in more tissues.
%
To test this hypothesis, I counted the number of unique transcription factors bound in a radius of 50 bp around each eQTL (Window of 100 bp).
%
eQTLs involved in 1, 2, 3 and 4 and more GWAS classes bind a mean number of 17,
19, 23 and 27 transcription factors, respectively (Fig. \ref{fig:freq_tf_per_variant}a).
%I found a significant larger number of transcription factors bound around pleiotropic variants (Fig. \ref{fig:freq_tf_per_variant}a).

### 2022-11-28 ms/ms04_discussion.tex
ENH updated with 418
MS

In this article, I present the results of a colocalization pipeline for eQTLs and GWAS variants that I have applied to a large number of 413 GWAS and 127 eQTL studies.
%
I have taken advantage of two public resources of GWAS and eQTL studies with summary statistics to compute a large number of colocalizations between eQTLs and GWAS variants.
%
These results are provided as a downloadable and an interactive table that can be used to explore variants with the GWAS traits, etissues and egenes.
%
For a posterior probability PP.H4.abf$\ge$0.8 of common causal eQTL and GWAS variants, we found 100,526 loci.
%
If I focus on causal variants with PP.H4.abf$\ge$0.8 and SNP.PP.H4$\ge$0.5, then I find 4684 variants.

This interactive table can be used for different applications.
%
For instance, egenes and etissues of colocalized eQTL variants provide potential predictions of the molecular mechanism of GWAs traits.
%
Colocalized loci provide predictions of potential causal variants in a given loci of GWAS.
%
The variant rs2107595 is in locus 7p21.1 downstream of the histone deacetylase 9 (HDAC9) is cardiovascular. Interestingly, it controls expression of lncRNA XXX that is not known in the context of cardiovascular diseases.

@@

@@

The raw colocalization data before filtering in a single file is available at this URL: \url{https://osf.io/hvmje}.
%
A website to access colocalization variants with PP.H4.abf $\geq$ 0.8 is available at this URL \url{https://agonzalez.pythonanywhere.com}.

>>>>

In this article, I present the results of a colocalization pipeline for eQTLs and GWAS variants that I have applied to 418 GWAS and 127 eQTL studies.
%
I have taken advantage of two public resources of GWAS and eQTL studies with summary statistics to compute a large number of colocalizations between eQTLs and GWAS variants.
%
We start with 10,627 tag variants with a significant p-value below 5e-8 and we observe a colocalization for 3,849 or 36\% of the leading variants from 335 GWAS.
%
More preciseley, in autoimmune diseases, we find colocalization for 37\% of leading GWAS variants, which is comparable
to a previous study that found colocalization for 40.4\% of GWAS loci \citep{2021.Li.Mu}.
%
The difference is that many colocalization by the previous study were contributed by RNA splicing, whereas our study entirely focuses on eQTLs.

These results are provided as a downloadable table that can be used to explore variants with the GWAS traits, eQTL tissues and genes.
%
We found 103,551 variants from 246 GWAS that colocalized with a posterior probability PP.H4.abf$\ge$0.8 with at least one eQTL.

%TODO continue

@@

% TODO comparison with watanabe pleiotropy study

% TODO comparison with genome biology colocalization paper

% This interactive table can be used for different applications.
% %
% For instance, egenes and etissues of colocalized eQTL variants provide potential predictions of the molecular mechanism of GWAs traits.
% %
% Colocalized loci provide predictions of potential causal variants in a given loci of GWAS.
% %
% The variant rs2107595 is in locus 7p21.1 downstream of the histone deacetylase 9 (HDAC9) is cardiovascular. Interestingly, it controls expression of lncRNA XXX that is not known in the context of cardiovascular diseases.

@@

The raw colocalization data before filtering in a single file is available at this URL: \url{https://osf.io/hvmje}.
%
A website to access colocalization variants with PP.H4.abf $\geq$ 0.5 is available at this URL: TODO.

### 2022-11-28 ms/ms06_floats.tex
MS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 2: Length histogram of regions
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/regions_100000_length_hist.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
\end{subfigure}
%
\caption{Analysis of pleiotropic regions. \textbf{a}, Length distribution of pleiotropic regions. \textbf{b}, Cumulative sum ordered inversely with the number of GWAS classes.} \label{fig:pleiotropy_region_distribution}
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 3: Histograms variants vs GWAS, eGene and eTissues
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
\end{subfigure}
%
\caption{Percentage of colocalized eQTL/GWAS variants with different number of GWAS classes (\textbf{a}), eQTL genes
    (\textbf{b}) and eQTL tissues (\textbf{c}).} \label{fig:hist_gwas_egene_etissue}
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 4: Scatter plots of winner regions
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{figure}[!tbp]

\begin{subfigure}[]{.24\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr11_start65488118_end65916060_categories7.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr12_start55721801_end56171027_categories6.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_gwas.py/count_per_rsid_chr19_start48668049_end48756272_categories6.png}
\end{subfigure}

\begin{subfigure}[]{.24\textwidth}
\textbf{e}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{f}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr11_start65488118_end65916060_categories7.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{g}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr12_start55721801_end56171027_categories6.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{h}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr19_start48668049_end48756272_categories6.png}
\end{subfigure}

\begin{subfigure}[]{.24\textwidth}
\textbf{i}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr5_start131912097_end132802472_categories7.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{j}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr11_start65488118_end65916060_categories7.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{k}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr12_start55721801_end56171027_categories6.png}
\end{subfigure}
%
\begin{subfigure}[]{.24\textwidth}
\textbf{l}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr19_start48668049_end48756272_categories6.png}
\end{subfigure}

\caption{Count of GWAS classes (\textbf{a-c}), eQTL genes (\textbf{d-f}) and eQTL tissues (\textbf{g-i}) in three
pleiotropic genomic regions: \textbf{a,e,i}: 5:131,912,097-132,802,472 (5q31.1), \textbf{b,f,j}: 11:65,488,118-65,916,060 (11q13.1),
    \textbf{c,g,k}: 12:55,721,801-56,171,027 (12q13.2), and \textbf{d,h,l}: 19:48,668,049-48,756,272 (19q13.33).
    Genomic coordinates are given for the hg38 assembly.}
\label{fig:region_gwas_egenes_tissues}
%
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 5: VEP consequences
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/vep.png}
%
\caption{Odds ratio of the variants annotated with given variant effect
predictor (VEP) consequence and given GWAS class count compared with non
pleiotropic variants with GWAS class count one. The significance is given for the
q-value with False discovery rate 5\%.}
\label{fig:vep_consequence}
%
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 6: Violin plots. eGenes, eTissues and gwas per variants
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
%\begin{subfigure}[]{.32\textwidth}
%\textbf{c}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_etissue_y_gwas.py/plt.png}
%\end{subfigure}
%
\caption{Mean number of genes in eQTL-tissue pairs (\textbf{a}) and mean number of tissues in eQTL-gene pairs (\textbf{b}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure}

@@

\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
\end{subfigure}
%
\caption{Analysis of transcription factor binding.
\textbf{a}, Binding count of transcription factors in the region surrounding pleiotropic eQTLs (Radius 50 bp) as a function of the GWAS class count.
\textbf{b}, Odds ratio of eQTLs annotated with cis regulatory modules vs non-annotated.} \label{fig:freq_tf_per_variant}
%
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 8: beta and log pval
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{figure}[!tbp]
%\centering
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{a}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_beta.py/eqtl_beta.png}
%\end{subfigure}
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{b}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_beta.py/gwas_beta.png}
%\end{subfigure}
%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{c}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_logpval.py/eqtl.png}
%\end{subfigure}
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{d}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_logpval.py/gwas.png}
%\end{subfigure}
%
%\caption{eQTL and GWAS effect size/beta (\textbf{a,b}) and eQTL and GWAS significance/p-value (\textbf{c,d}) as a function of the GWAS class count.} \label{fig:beta_pval}
%%
%\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 2: Length histogram of regions
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/regions_100000_length_hist.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
\end{subfigure}
%
\caption{Analysis of pleiotropic regions. \textbf{a}, Length distribution of pleiotropic regions. \textbf{b}, Cumulative sum ordered inversely with the number of GWAS classes.} \label{fig:pleiotropy_region_distribution}
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 3: Histograms variants vs GWAS, eGene and eTissues
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
\end{subfigure}
%
\caption{Percentage of colocalized eQTL/GWAS variants with different number of GWAS classes (\textbf{a}), eQTL genes
    (\textbf{b}) and eQTL tissues (\textbf{c}).} \label{fig:hist_gwas_egene_etissue}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 4: Correlation between GWAS, genes and tissue counts
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\includegraphics[width=0.7\textwidth]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_egene_etissue_corr.png}
%
\caption{Spearman correlation between the counts of GWAS classes, eQTL genes and eQTL tissues.}
\label{fig:correlation_counts}
%
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 5: VEP consequences
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/vep.png}
%
\caption{Odds ratio of the variants annotated with given variant effect
predictor (VEP) consequence and given GWAS class count compared with non
pleiotropic variants with GWAS class count one. The significance is given for the
q-value with False discovery rate 5\%.}
\label{fig:vep_consequence}
%
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 6: Violin plots. eGenes, eTissues and gwas per variants
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
%\begin{subfigure}[]{.32\textwidth}
%\textbf{c}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_etissue_y_gwas.py/plt.png}
%\end{subfigure}
%
\caption{Mean number of genes in eQTL-tissue pairs (\textbf{a}) and mean number of tissues in eQTL-gene pairs (\textbf{b}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure}

@@

\begin{figure}[!tbp]
\centering
%
\begin{subfigure}[]{.33\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbox_x_per_rsid_y_remapnr.py/bxplt_remaptf_per_rsid_flank_10.png}
\end{subfigure}
%
\begin{subfigure}[]{.33\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_pleiotropy_y_remapcrm.py/remapcrm_flank10.png}
\end{subfigure}
%
\caption{Analysis of transcription factor binding.
\textbf{a}, Binding count of transcription factors in the region surrounding pleiotropic eQTLs with a radius of 50 bp as a function of the GWAS class count.
\textbf{b}, Odds ratio of eQTLs annotated as belonging to a cis regulatory modules vs non-annotated.} \label{fig:freq_tf_per_variant}
%
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 8: beta and log pval
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{figure}[!tbp]
%\centering
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{a}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_beta.py/eqtl_beta.png}
%\end{subfigure}
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{b}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_beta.py/gwas_beta.png}
%\end{subfigure}
%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{c}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_logpval.py/eqtl.png}
%\end{subfigure}
%%
%\begin{subfigure}[]{.33\textwidth}
%\textbf{d}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_gwas_cat_y_logpval.py/gwas.png}
%\end{subfigure}
%
%\caption{eQTL and GWAS effect size/beta (\textbf{a,b}) and eQTL and GWAS significance/p-value (\textbf{c,d}) as a function of the GWAS class count.} \label{fig:beta_pval}
%%Correlation
%\end{figure}
